Fusing Filters with Integer Linear Programming

### 2014-05-16 2014betterfusionforfilters/section/06-Related.tex
related work: darte formulation

%!TEX root = ../Main.tex
\section{Related Work}
The idea of using integer linear programming to cluster an operator graph for array fusion was first fully described by Megiddo and Sarkar~\cite{megiddo1998optimal}~(1999). This algorithm was then extended to support multiple iteration sizes by Darte and Huard~\cite{darte2002contraction}. Both algorithms were developed in the context of imperative languages (Fortran) and are based around a Loop Dependence Graph (LDG). In a LDG the nodes represent imperative loops, and the edges indicate which loops may or may not be fused. Although this work was developed in a context of imperative programming, the conceptual framework and algorithms are language agnostic. In earlier work, Chatterjee~\cite{chatterjee1993nested} (1991) mentioned that ILP can be used to schedule a data flow graph, though did not give a complete formulation. Our system extends the prior ILP approaches with support for size changing operators such as @filter@.

>>>>

%!TEX root = ../Main.tex
\section{Related Work}
The idea of using integer linear programming to cluster an operator graph for array fusion was first fully described by Megiddo and Sarkar~\cite{megiddo1998optimal}~(1999).  A simpler formulation, supporting only loops of the same iteration size, but optimizing for array contraction, was then described by Darte and Huard~\cite{darte2002contraction}~(2002).  Both algorithms were developed in the context of imperative languages (Fortran) and are based around a Loop Dependence Graph (LDG).  In a LDG the nodes represent imperative loops, and the edges indicate which loops may or may not be fused.  Although this work was developed in a context of imperative programming, the conceptual framework and algorithms are language agnostic. In earlier work, Chatterjee~\cite{chatterjee1993nested} (1991) mentioned that ILP can be used to schedule a data flow graph, though did not give a complete formulation. Our system extends the prior ILP approaches with support for size changing operators such as @filter@.
